\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.375in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\href{https://www.linkedin.com/in/xairaven}{\Large Oleksandr Kovalov}} & Location: Kropyvnytskyi or Kyiv \\
  \href{https://www.linkedin.com/in/xairaven}{{https://www.linkedin.com/in/xairaven}} & Email: \href{mailto:oleksandr.kovalov.work@gmail.com}{oleksandr.kovalov.work@gmail.com} \\ & Mobile: \href{tel:+380957365160}{+38 095 736 51 60} \\ &
  GitHub: \href{https://www.github.com/xairaven}{github.com/xairaven}
\end{tabular*}

%--------PROGRAMMING SKILLS------------
\section{Skills}
\resumeSubHeadingListStart
\item{
	\textbf{English}{: B1 \textbf{(Spoken \& Written)}, B2-C1 \textbf{(Reading \& Listening)} }
}
\item{
	Rust \textit{(Primary Language)}, C\# \textit{(WPF)}, Java, C, Bash, Docker, Linux \textit{(Ubuntu Server, CentOS, Oracle Server)}, OOP, SOLID, SQL \textit{(SQLite, MS SQL, MySQL, MariaDB)}, Python, Apache, Networking, Git, WASM, Algorithms \& Data Structures, UML, Github Actions.
}
\resumeSubHeadingListEnd

%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Igor Sikorsky Kyiv Polytechnic Institute}{Kyiv}
      {Bachelor, Computer Science -- Digital Technologies in Energy}{Sep. 2021 -- Jun. 2025}
    \resumeSubheading
    	{Igor Sikorsky Kyiv Polytechnic Institute}{Kyiv}
    	{Master \textbf{(Currently Studying)}, SWE -- Computer Systems Software Engineering}{Sep. 2025 -- \textbf{Jun. 2027}}
  \resumeSubHeadingListEnd

%-----------EXPERIENCE-----------------
\section{Experience}
\resumeSubHeadingListStart

\resumeSubheading
{KPI-Craft}{Kyiv}
{System Admin, Owner}{Oct 2024 - Present}
\resumeItemListStart
\resumeItem{System Administering}
	{Deployed a Linux server, handled monitoring, backups, set up plugin system.}
\resumeItem{CEO}
	{I founded the project, managed user support \& advertising of it.}
\resumeItem{Security}
	{Successfully repelled several attacks on the infrastructure.}
\resumeItemListEnd

\resumeSubHeadingListEnd

%-----------PROJECTS-----------------
\section{Projects}
  \resumeSubHeadingListStart
    \resumeSubItem{xailyser -- Rust, libpcap, nom, WebSocket, egui}
      {\\ A modular deep packet inspection platform built in Rust, comprising a core DPI library for packet capture and protocol parsing (libpcap + nom), a multithreaded backend server that aggregates traffic statistics and streams JSON frames over WebSockets, and a cross‑platform egui desktop client displaying real‑time charts, device aliases, OUI vendor lookups, and packet details, demonstrating expertise in systems‑level Rust, network protocols, concurrency, and UI development. \\
      \textbf{Link}:  \href{https://github.com/xairaven/xailyser}{github.com/xairaven/xailyser}
	}
	\resumeSubItem{xArpChat -- Rust, Networks}
	{\\ A lightweight peer-to-peer chat application written in Rust, leveraging ARP (Address Resolution Protocol) for local network communication. It features message broadcasting without requiring a centralized server, demonstrating proficiency in low-level networking and Rust's concurrency model. Used Cursive as TUI library. Also used PNet, Crossbeam, smaz, thiserror libraries. Made Github Actions workflow for building \& creating releases. \\
		\textbf{Link}:  \href{https://github.com/xairaven/arpchat-rs}{github.com/xairaven/arpchat-rs}
	}
	\resumeSubItem{FractalRenderer -- Rust, WebAssembly}
	{\\ A Rust-based visualization tool for generating IFS (Iterated Function System) and L-System fractals, originally two separate university lab projects merged into a single codebase. It offers both native GUI via egui and browser-based rendering through WebAssembly, highlighting your experience with Rust’s frontend ecosystems and cross-platform deployment. \\
		\textbf{Link}: \href{https://github.com/xairaven/FractalRenderer}{github.com/xairaven/FractalRenderer}
	}
	\resumeSubItem{Blood Bank Management -- Linux, Apache, Docker, Ansible \textit{(Not my project, just deployment)}}
	{\\ Blood Bank Management System using PHP, MySQL, HTML, CSS3 + Bootstrap. Deployed it on two local virtual machines in several variants: Manually started Apache on the first and created MySQL DB on the second; Docker + Docker-Compose variant; Configuration set up with Ansible. \\
		\textbf{Link}:  \href{https://github.com/xairaven/BBMS-Deploy}{github.com/xairaven/BBMS-Deploy}
	}
  \resumeSubHeadingListEnd
  
  %-----------Certificates-----------------
\section{Certificates}
  \resumeSubHeadingListStart
    \resumeSubItem{Linux \& Network Administration}
	    {PortaOne, 2024}
     \resumeSubItem{DevOps Crash Course}
	    {SoftServe, 2023}
	 \resumeSubItem{English Certificate 71/100}
	 	{EF Set, June 2023}
  \resumeSubHeadingListEnd

%-------------------------------------------
\end{document}
